Dynamical modeling of tidal streams

### 2014-01-08 tex/ms.tex
streams: fix L-LZ abs

In particular, because for any spherical potential $\Phi^A$ we have
that $J_Z = |L|-L_Z$, independent of the particular form of $\Phi^A$,
\equationname~(\ref{eq:aAIJ}) implies that as long as there is a
spherical auxiliary potential in which the auxiliary angle
$\theta^A_Z$ goes through the full range $0$ to $2\pi$ along the orbit
integrated in a general potential, $J_Z$ can be obtained by averaging
$|L|-L_Z$ over the orbit. Similarly, as $J_\phi = L_Z$ for any
axisymmetric potential, we can approximate $J_\phi$ for any triaxial
potential by averaging $L_Z$ over the orbit, as long as an auxiliary
axisymmetric potential exists in which $\theta^A_\phi$ goes through
the full range $0$ to $2\pi$ along the orbit (\ie, if the orbit is a
loop orbit).

>>>>

In particular, because for any spherical potential $\Phi^A$ we have
that $J_Z = L-|L_Z|$, independent of the particular form of $\Phi^A$,
\equationname~(\ref{eq:aAIJ}) implies that as long as there is a
spherical auxiliary potential in which the auxiliary angle
$\theta^A_Z$ goes through the full range $0$ to $2\pi$ along the orbit
integrated in a general potential, $J_Z$ can be obtained by averaging
$L-|L_Z|$ over the orbit. Similarly, as $J_\phi = L_Z$ for any
axisymmetric potential, we can approximate $J_\phi$ for any triaxial
potential by averaging $L_Z$ over the orbit, as long as an auxiliary
axisymmetric potential exists in which $\theta^A_\phi$ goes through
the full range $0$ to $2\pi$ along the orbit (\ie, if the orbit is a
loop orbit).
